Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications

### 2018-03-08 scnn.tex
experiments & data

@@

\section{Experiments}
\assign{Nathanaël, Tomek}

@@

>>>>

Show the spherical harmonics.

@@

\section{Experiments}

What do we want to show? The graph CNN is able to discriminate ??? using higher order statistics.

\subsection{Data}
\assign{Tomek}

Our data comes from a simulation with software ??? using the following parameters ???. All the data to reproduce our experiments are available online.\footnote{\url{https://doi.org/10.5281/zenodo.????} \todo{correct DOI}}

\subsection{Results}
\assign{Nathanaël, Tomek}

@@

\subsection{Interpretation}
\assign{Nathanaël, Tomek, Michaël}

Show the learned filters and feature maps and try to interpret them.
